---
title: "14mer oligo selection"
author: "Max Trauernicht"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_document:
    theme: journal #cerulean
    highlight: monochrome
    toc: true
    toc_float: true
    code_folding: show
  editor_options:
    chunk_output_type: console
---

# knitr document van Steensel lab

# 14-mer oligo design

# Introduction
The aim of this script is to design oligos that can probe the activity of all possible 14-mers. A great part of this script will focus on selecting potentially relevant 14-mers.

## Description of Data
How to make a good rendering table: 
```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| column1	|	column2	|	column3	|	
|----|----|----|
|1	|	2	|	3	|	
|a	|	b	|	c	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

# Data processing
## Path, Libraries, Parameters and Useful Functions
```{r setup}
knitr::opts_chunk$set(echo = TRUE)
StartTime <-Sys.time()

# 8-digit Date tag:
Date <- substr(gsub("-","",Sys.time()),1,8) 
# libraries:
library(gtools)
library(BSgenome)
library(BiocManager)
```

### Custom functions
Functions used thoughout this script.
```{r}
SetFileName <- function(filename, initials) {
  # Set filename with extension and initials to make filename with date integrated.
  filename <- substitute(filename)
  initials <- substitute(initials)
  filename <- paste0(initials, Date, filename)
  filename
}
```


## Data import
```{r}
# Import top 1,000 14-mers that occur most frequently in mm10

# Fede's self-curated .meme TF information

# Fede's non-composite TF selection

```


## Data import
```{r}
# Create all possible 14-mers using python
```


## Data import
```{r}
# Create all possible 14-mers using python
```


# Analysis

## Mouse genome mapping
```{r}

```

## TF motif scanning
```{r}
# Run FIMO script - extract all no matches

# Compute distance of no matches with TF motif db
matchPWM()

```





# Results
```{r}
```

# Conclusions
```{r}
```

## Exporting potential data. 
```{r}
```

# Session Info
```{r}
paste("Run time: ",format(Sys.time()-StartTime))
getwd()
date()
sessionInfo()
```

